---
title: "EE232E P2"
## Part 1: Facebook Network
---

Relevent Packages
```{r}
library('igraph')
library('Matrix')
```

### 1 Facebook network

#### 1.1 Structural properties of the facebook network

##### Q1
```{r}
FB <- read_graph("facebook_combined.txt",format="edgelist",directed=FALSE)
fc <- cluster_fast_greedy(FB)

plot(fc,FB,vertex.size=5, vertex.label=NA)
is.connected(FB)
```

##### Q2
```{r}
print(diameter(FB, directed = FALSE, unconnected = FALSE))
```

##### Q3
```{r}
plot(degree.distribution(FB),main="Degree distribution of the network",xlab="Degree",ylab="Frequency")
print(mean(degree(FB)))
```

##### Q4
```{r}
# Learn from it!!!
fit_power_law = function(graph) {
    # calculate degree
    d = degree(graph, mode = "all")
    dd = degree.distribution(graph, mode = "all", cumulative = FALSE)
    degree = 1:max(d)
    probability = dd[-1]
    # delete blank values
    nonzero.position = which(probability != 0)
    probability = probability[nonzero.position]
    degree = degree[nonzero.position]
    reg = lm(log(probability) ~ log(degree))
    cozf = coef(reg)
    power.law.fit = function(x) exp(cozf[[1]] + cozf[[2]] * log(x))
    alpha = cozf[[2]]
    R.square = summary(reg)$r.squared
    print(paste("slope =", round(alpha, 3)))
    
    # plot
    plot(probability ~ degree, log = "xy", xlab = "Degree (log)", ylab = "Probability (log)", 
        col = 1, main = "Degree Distribution")
    #abline(mod <- lm(log(probability) ~ log(degree)))
    curve(power.law.fit, col = "red", add = T, n = length(d))
    
}


fit_power_law(FB)
```


#### 1.2 Personalized network

##### Q5
```{r}
FB_neighbor1=neighbors(FB, 1, mode = "total")
FB_id1=induced_subgraph(FB, c(1,FB_neighbor1), impl ="auto")
vcount(FB_id1)
ecount(FB_id1)
```

##### Q6
```{r}
print(diameter(FB_id1, directed = FALSE, unconnected = FALSE))
```
Trivial upper and lower bound: 0 (lower bound: when the selected node has no neighbours) and 8(upper bound: diameter of the whole network).

##### Q7

- Lower bound: 0, which means the selected node has no neighbour.
- Upper bound: diameter of the whole network (8 in this case), all the nodes are a friend of the selected node.

#### 1.3 Core node’s personalized network

##### Q8
```{r}
core=c()
deg=c()
for( v in V(FB)){
    if(length(neighbors(FB, v, mode = "total"))>200){
        core=append(core,v)
        deg=append(deg,degree(FB,v))
        }
}
print(length(core)) # Number of core nodes
print(mean(deg)) # Average degree of core nodes
```

##### Q9
Plot Function
```{r}
plotCommunity = function(com,graph) {
    colors = rainbow(max(membership(com))+1)
    #print(membership(com))
    nodes_colors = colors[1:(length(colors)-1)]
    V(graph)$color = nodes_colors[membership(com)] 
    V(graph)$size= 5
    V(graph)[1]$color = colors[length(colors)] 
    V(graph)[1]$size = 15
    print(paste("modularity score =", modularity(com)))
    plot(graph,vertex.label=NA)
}
```
Node 1
```{r}
# fast greedy for FB_1
com1FG=cluster_fast_greedy(FB_id1, merges = FALSE, modularity = TRUE,
 weights=NULL)
plotCommunity(com1FG,FB_id1)
```

```{r}
# Edge-Betweenness for FB_1
com1EB = cluster_edge_betweenness(FB_id1,weights=NULL, directed=FALSE,modularity=TRUE)
plotCommunity(com1EB,FB_id1)
```
```{r}
# Infomap for FB_1
com1IC = infomap.community(FB_id1)
plotCommunity(com1IC,FB_id1)
```
Generate subgraphs for the other four core nodes
```{r}
FB_id_108=induced_subgraph(FB, c(108,neighbors(FB, 108, mode = "total")), impl ="auto")
FB_id_349=induced_subgraph(FB, c(349,neighbors(FB, 349, mode = "total")), impl ="auto")
FB_id_484=induced_subgraph(FB, c(484,neighbors(FB, 484, mode = "total")), impl ="auto")
FB_id_1087=induced_subgraph(FB, c(1087,neighbors(FB, 1087, mode = "total")), impl ="auto")
```

Node 108
```{r}
# fast greedy for FB_108
com108FG=cluster_fast_greedy(FB_id_108, merges = FALSE, modularity = TRUE,  weights=NULL)
plotCommunity(com108FG,FB_id_108)

# Run extremely slow!! Or something wrong???
# Edge-Betweenness for FB_108
com108EB = cluster_edge_betweenness(FB_id_108,weights=NULL,directed=FALSE, modularity=TRUE)
plotCommunity(com108EB,FB_id_108)

# Infomap for FB_108
com108IC = infomap.community(FB_id_108)
plotCommunity(com108IC,FB_id_108)
```


Node 349
```{r}
# fast greedy for FB_349
com349FG=cluster_fast_greedy(FB_id_349, merges = FALSE, modularity = TRUE,
 weights=NULL)
plotCommunity(com349FG,FB_id_349)

# Edge-Betweenness for FB_349
com349EB = cluster_edge_betweenness(FB_id_349,weights=NULL, directed=FALSE,modularity=TRUE)
plotCommunity(com349EB,FB_id_349)

# Infomap for FB_349
com349IC = infomap.community(FB_id_349)
plotCommunity(com349IC,FB_id_349)
```

Node 484
```{r}
# fast greedy for FB_484
com484FG=cluster_fast_greedy(FB_id_484, merges = FALSE, modularity = TRUE,
 weights=NULL)
plotCommunity(com484FG,FB_id_484)

# Edge-Betweenness for FB_484
com484EB = cluster_edge_betweenness(FB_id_484,weights=NULL, directed=FALSE,modularity=TRUE)
plotCommunity(com484EB,FB_id_484)

# Infomap for FB_484
com484IC = infomap.community(FB_id_484)
plotCommunity(com484IC,FB_id_484)
```

Node 1087
```{r}
# fast greedy for FB_1087
com1087FG=cluster_fast_greedy(FB_id_1087, merges = FALSE, modularity = TRUE,
 weights=NULL)
plotCommunity(com1087FG,FB_id_1087)

# Edge-Betweenness for FB_1087
com1087EB = cluster_edge_betweenness(FB_id_1087,weights=NULL, directed=FALSE,modularity=TRUE)
plotCommunity(com1087EB,FB_id_1087)

# Infomap for FB_1087
com1087IC = infomap.community(FB_id_1087)
plotCommunity(com1087IC,FB_id_1087)
```



##### Q10
```{r}
FB_id1_WC = induced_subgraph(FB, c(neighbors(FB, 1, mode = "total")), impl ="auto")
FB_id_108_WC = induced_subgraph(FB, c(neighbors(FB, 108, mode = "total")), impl ="auto")
FB_id_349_WC = induced_subgraph(FB, c(neighbors(FB, 349, mode = "total")), impl ="auto")
FB_id_484_WC = induced_subgraph(FB, c(neighbors(FB, 484, mode = "total")), impl ="auto")
FB_id_1087_WC = induced_subgraph(FB, c(neighbors(FB, 1087, mode = "total")), impl ="auto")

```
Node 1
```{r}
# fast greedy
com1FG_WC=cluster_fast_greedy(FB_id1_WC, merges = FALSE, modularity = TRUE,
 weights=NULL)
plotCommunity(com1FG_WC,FB_id1_WC)

# Edge-Betweenness
com1EB_WC = cluster_edge_betweenness(FB_id1_WC,weights=NULL, directed=FALSE,modularity=TRUE)
plotCommunity(com1EB_WC,FB_id1_WC)

# Infomap for
com1IC_WC = infomap.community(FB_id1_WC)
plotCommunity(com1IC_WC,FB_id1_WC)
```
Node 108
```{r}
# fast greedy for FB_108
com108FG_WC=cluster_fast_greedy(FB_id_108_WC, merges = FALSE, modularity = TRUE,  weights=NULL)
plotCommunity(com108FG_WC,FB_id_108_WC)

# Run extremely slow!! Or something wrong???
# Edge-Betweenness for FB_108
com108EB_WC = cluster_edge_betweenness(FB_id_108_WC,weights=NULL,directed=FALSE, modularity=TRUE)
plotCommunity(com108EB_WC,FB_id_108_WC)

# Infomap for FB_108
com108IC_WC = infomap.community(FB_id_108_WC)
plotCommunity(com108IC_WC,FB_id_108_WC)
```

Node 349
```{r}
# fast greedy for FB_349
com349FG_WC=cluster_fast_greedy(FB_id_349_WC, merges = FALSE, modularity = TRUE,
 weights=NULL)
plotCommunity(com349FG_WC,FB_id_349_WC)

# Edge-Betweenness for FB_349
com349EB_WC = cluster_edge_betweenness(FB_id_349_WC,weights=NULL, directed=FALSE,modularity=TRUE)
plotCommunity(com349EB_WC,FB_id_349_WC)

# Infomap for FB_349
com349IC_WC = infomap.community(FB_id_349_WC)
plotCommunity(com349IC_WC,FB_id_349_WC)
```

Node 484
```{r}
# fast greedy for FB_484
com484FG_WC=cluster_fast_greedy(FB_id_484_WC, merges = FALSE, modularity = TRUE,
 weights=NULL)
plotCommunity(com484FG_WC,FB_id_484_WC)

# Edge-Betweenness for FB_484
com484EB_WC = cluster_edge_betweenness(FB_id_484_WC,weights=NULL, directed=FALSE,modularity=TRUE)
plotCommunity(com484EB_WC,FB_id_484_WC)

# Infomap for FB_484
com484IC_WC = infomap.community(FB_id_484_WC)
plotCommunity(com484IC_WC,FB_id_484_WC)
```

Node 1087
```{r}
# fast greedy for FB_1087
com1087FG_WC=cluster_fast_greedy(FB_id_1087_WC, merges = FALSE, modularity = TRUE,
 weights=NULL)
plotCommunity(com1087FG_WC,FB_id_1087_WC)

# Edge-Betweenness for FB_1087
com1087EB_WC = cluster_edge_betweenness(FB_id_1087_WC,weights=NULL, directed=FALSE,modularity=TRUE)
plotCommunity(com1087EB_WC,FB_id_1087_WC)

# Infomap for FB_1087
com1087IC_WC = infomap.community(FB_id_1087_WC)
plotCommunity(com1087IC_WC,FB_id_1087_WC)
```

##### Q11

Typically, the embeddedness of a node is larger if its degree is higher. With higher degree, the node will have more neighbours, thus a higher probability to have more mutual connections with the core node. 

##### Q12

```{r}
# !!!Here, when calculating dispersion, we did not remove the node to be calculated from the network (the core node does be removed), which may cause some problem???
core_node_vec <- list(1,108,349,484,1087)
FB_vec <- list(FB_id1,FB_id_108,FB_id_349,FB_id_484,FB_id_1087)
FB_WC_vec <- list(FB_id1_WC,FB_id_108_WC,FB_id_349_WC,FB_id_484_WC,FB_id_1087_WC)
#embeddedness_vec <- rep(rep(0, length(V(FB_id1_WC))),5)
#dispersion_vec <- rep(rep(0, length(V(FB_id1_WC))),5)
# Node 1
embeddedness_vec_1 <- rep(0, length(V(FB_id1_WC)))
dispersion_vec_1 <- rep(0, length(V(FB_id1_WC)))
for(vv in V(FB_id1_WC)){
  neighbor_temp = neighbors(FB_id1_WC, vv, mode = "total")
  embeddedness_vec_1[vv] <- length(intersect(neighbor_temp,V(FB_id1_WC)))
  modefied_net <- delete_vertices(FB_id1_WC,vv)
  dis_temp <- 0
  for (i in neighbor_temp){
    for (j in neighbor_temp){
      dis_temp <- dis_temp + distances(FB_id1_WC, v = i, to = j)[1]
    }
  }
  dispersion_vec_1[vv] <- dis_temp
}
dispersion_vec_1 <- dispersion_vec_1/2
plot(density(embeddedness_vec_1),main="Embeddedness Distribution for Node 1's Personalized Network",xlab="Embeddedness")
plot(density(dispersion_vec_1),main="Dispersion Distribution for Node 1's Personalized Network",xlab="Dispersion")

# Node 108
embeddedness_vec_108 <- rep(0, length(V(FB_id_108_WC)))
dispersion_vec_108 <- rep(0, length(V(FB_id_108_WC)))
for(vv in V(FB_id_108_WC)){
  neighbor_temp = neighbors(FB_id_108_WC, vv, mode = "total")
  embeddedness_vec_108[vv] <- length(intersect(neighbor_temp,V(FB_id_108_WC)))
  modefied_net <- delete_vertices(FB_id_108_WC,vv)
  dis_temp <- 0
  for (i in neighbor_temp){
    for (j in neighbor_temp){
      dis_temp <- dis_temp + distances(FB_id_108_WC, v = i, to = j)[1]
    }
  }
  dispersion_vec_108[vv] <- dis_temp
}
dispersion_vec_108 <- dispersion_vec_108/2
plot(density(embeddedness_vec_108),main="Embeddedness Distribution for Node 108's Personalized Network",xlab="Embeddedness")
plot(density(dispersion_vec_108),main="Dispersion Distribution for Node 108's Personalized Network",xlab="Dispersion")

# Node 349
embeddedness_vec_349 <- rep(0, length(V(FB_id_349_WC)))
dispersion_vec_349 <- rep(0, length(V(FB_id_349_WC)))
for(vv in V(FB_id_349_WC)){
  neighbor_temp = neighbors(FB_id_349_WC, vv, mode = "total")
  embeddedness_vec_349[vv] <- length(intersect(neighbor_temp,V(FB_id_349_WC)))
  modefied_net <- delete_vertices(FB_id_349_WC,vv)
  dis_temp <- 0
  for (i in neighbor_temp){
    for (j in neighbor_temp){
      dis_temp <- dis_temp + distances(FB_id_349_WC, v = i, to = j)[1]
    }
  }
  dispersion_vec_349[vv] <- dis_temp
}
dispersion_vec_349 <- dispersion_vec_349/2
plot(density(embeddedness_vec_349),main="Embeddedness Distribution for Node 349's Personalized Network",xlab="Embeddedness")
plot(density(dispersion_vec_349),main="Dispersion Distribution for Node 349's Personalized Network",xlab="Dispersion")

# Node 484
embeddedness_vec_484 <- rep(0, length(V(FB_id_484_WC)))
dispersion_vec_484 <- rep(0, length(V(FB_id_484_WC)))
for(vv in V(FB_id_484_WC)){
  neighbor_temp = neighbors(FB_id_484_WC, vv, mode = "total")
  embeddedness_vec_484[vv] <- length(intersect(neighbor_temp,V(FB_id_484_WC)))
  modefied_net <- delete_vertices(FB_id_484_WC,vv)
  dis_temp <- 0
  for (i in neighbor_temp){
    for (j in neighbor_temp){
      dis_temp <- dis_temp + distances(FB_id_484_WC, v = i, to = j)[1]
    }
  }
  dispersion_vec_484[vv] <- dis_temp
}
dispersion_vec_484 <- dispersion_vec_484/2
plot(density(embeddedness_vec_484),main="Embeddedness Distribution for Node 484's Personalized Network",xlab="Embeddedness")
plot(density(dispersion_vec_484),main="Dispersion Distribution for Node 484's Personalized Network",xlab="Dispersion")


# Node 1087
embeddedness_vec_1087 <- rep(0, length(V(FB_id_1087_WC)))
dispersion_vec_1087 <- rep(0, length(V(FB_id_1087_WC)))
for(vv in V(FB_id_1087_WC)){
  neighbor_temp = neighbors(FB_id_1087_WC, vv, mode = "total")
  embeddedness_vec_1087[vv] <- length(intersect(neighbor_temp,V(FB_id_1087_WC)))
  modefied_net <- delete_vertices(FB_id_1087_WC,vv)
  dis_temp <- 0
  for (i in neighbor_temp){
    for (j in neighbor_temp){
      dis_temp <- dis_temp + distances(FB_id_1087_WC, v = i, to = j)[1]
    }
  }
  dispersion_vec_1087[vv] <- dis_temp
}
dispersion_vec_1087 <- dispersion_vec_1087/2
plot(density(embeddedness_vec_1087),main="Embeddedness Distribution for Node 1087's Personalized Network",xlab="Embeddedness")
plot(density(dispersion_vec_1087),main="Dispersion Distribution for Node 1087's Personalized Network",xlab="Dispersion")

```


##### Q13 & Q14


```{r}
nodeAndEdge = function(g, id,com){
    colors = rainbow(max(membership(com))+1)
    #print(membership(com))
    nodes_colors = colors[1:(length(colors)-1)]
    V(g)[id]$color <- "blue"
    temp=E(g) [ from(id) ]
    V(g)$color = nodes_colors[membership(com)] 
    E(g)[ inc(id)]$color <- 'blue'
    V(g)$size= 2
    plot(g,vertex.size=2,vertex.label=NA)
}
nodeAndEdge(FB_id1_WC, which.max(embeddedness_vec_1),com1FG_WC)
nodeAndEdge(FB_id_108_WC, which.max(embeddedness_vec_108),com108FG_WC)
nodeAndEdge(FB_id_349_WC, which.max(embeddedness_vec_349),com349FG_WC)
nodeAndEdge(FB_id_484_WC, which.max(embeddedness_vec_484),com484FG_WC)
nodeAndEdge(FB_id_1087_WC, which.max(embeddedness_vec_1087),com1087FG_WC)




```
```{r}
nodeAndEdge(FB_id1_WC, which.max(dispersion_vec_1),com1FG_WC)
nodeAndEdge(FB_id_108_WC, which.max(dispersion_vec_108),com108FG_WC)
nodeAndEdge(FB_id_349_WC, which.max(dispersion_vec_349),com349FG_WC)
nodeAndEdge(FB_id_484_WC, which.max(dispersion_vec_484),com484FG_WC)
nodeAndEdge(FB_id_1087_WC, which.max(dispersion_vec_1087),com1087FG_WC)
```
```{r}
nodeAndEdge(FB_id1_WC, which.max(dispersion_vec_1/embeddedness_vec_1),com1FG_WC)
nodeAndEdge(FB_id_108_WC, which.max(dispersion_vec_108/embeddedness_vec_108),com108FG_WC)
nodeAndEdge(FB_id_349_WC, which.max(dispersion_vec_349/embeddedness_vec_349),com349FG_WC)
nodeAndEdge(FB_id_484_WC, which.max(dispersion_vec_484/embeddedness_vec_484),com484FG_WC)
nodeAndEdge(FB_id_1087_WC, which.max(dispersion_vec_1087/embeddedness_vec_1087),com1087FG_WC)
```
